caDDS: Community Assisted Distributed Database for Sequences

### 2020-06-24 Paper2020ACM/Paper2020.tex
Revision June 24 630pm
Revision June 24 1030pm

An important aspect of the proposed system is the transfer of files to other computers. To achieve that, there are network technologies and systems that need to be understood. Each layer of the network has certain features, securities, and abstraction which contributes to the overall idea of sharing files across networks. Networks Layers are the abstraction of how computers pass data to each other. Understanding this is needed to maximize the speed in which data is transferred between computers. As well as to realize where certain problems or bottlenecks later on. A network, specifically the Internet, is comprised of the following levels of abstraction. \cite{kurose}
\begin{enumerate}
    \item Level 1: Medium used to send signals (physical, electrical signals of 0
and 1), through wire or by air
    \item Level 2: Introduction of packets: Wifi, Ethernet, connecting together
different . Goal of sending a group of signals.
    \item Level 3: Introduction of networks: IP Address to uniquely identify
entities.
    \item Level 4: Management of error free data transmission: Sending a group
of messages via TCP, UDP, FTP
    \item Level 5: Abstraction of Level 4: Function calls programmers will use
to do level 4 processes.
\end{enumerate}

@@

The database is a distributed database, which will aim to utilize the best features from Peer2Peer and Client/Servers. This will also aim to store sequences. Thus the "Distributed Database for Sequences" portion of the title.

\subsubsection{Community Aspect} \label{community}
The sytem was also described as community assisted. The definition of \textbf{community} to be used here is a \textit{set of people who generally collaborate together to do research}. And the focus is the genome research community. Reemphasizing certain features from the database, that any users can upload data. This means all users in the community can contribute to the knowledge base, and contribute data to be used by the community. Another important community aspect is that users can become data nodes themselves. Meaning these users can increase the overall storage of the database, and at the same time theoretically increase data speeds (which will be discussed more later). Frequently used local data as well will be more easily accessible (since it's on local data nodes, and should have faster access speeds). The concept of closer networks having faster speeds (discussed in the network section) is at play here. Another community aspect will be this paper, publicly describing many aspects of the structure and code. So that this concept may be further developed and even implemented by genome research communities.

@@

For the final comparisons of the base method the proposed method, the current base method (NCBI in Section \ref{NCBI}) is the go-to website for biological data and genomic data. It is currently used by and is one website and one server. This points to a single point of failure\cite{seqtorr}. The section \ref{theoreticalspeed} on theoretical analysis of speed described the problem of having a bottleneck when the number of users are too many for the data bandwidth of the server.

@@

\section{User-System Interface}
(check appendix for detailed pseudocode)

parang this section abstracts the user part from the system part

The user commmunicates with the system. User can do create, read, update, delete.

The system on its own delegates how things are stored or updated consistently ...

The user communicates with the master all the time???

\section{Master Node-Data Node Interface}
(check appendix for detailed pseudocode)

parang this section abstracts how master and data communicate and store data

GET
The user requests data from the system (via the master gate hehe)

The master holds a copy of all the data locations in the data nodes (can be called a directory). 
The master once needs a certain data, will check its directory which data nodes have it
The master once knows which of its data nodes have the data (multiple) will call them to inform it will request data
The data is informed that data will be requests
The master sends the directory of addresses of data nodes with the data and transfer key???? to the user

The user user receives the transfer key and uses it in the website to request data from data nodes

CREATE
The user wants to send data to the system (via the master gate hehe)

The master holds a copy of all the data locations (can be called a directory). 
The master will find 2+ data nodes to hold the data, and store them in a temp directory
The master will call the 2+ data nodes and check if they have enough space and are able to receive the data
The master will wait for an ack before sending the data to the 2+ data nodes
The master will ask the user to generate a hashcode
The master will send the user data nodes to send the data
The data nodes will receive the data and hash
The data nodes will complete receiving data, generate a hash and compare it with the user's hash. If different, repeat the process (may ask from a data node with complete data).
The data nodes if all have the complete, correct data will inform master node.

The user user receives the transfer key 
The user generates a hash of its data
The user uses the transfer key to send data to data nodes

\section{Master Node-Data Node Structure}
(check appendix for detailed pseudocode)

MASTER NODE
holds data:
directory of data nodes with verified data
directory of data nodes with unverified data (being transferred currently)
directory of data nodes space free

holds function:
which data nodes have data x?
does data node N have data x?
is user able to receive data X?
is user able to send data X?
is data node N able to send data X?
is data node N able to receive data X?

what is hash of data X on data node N?
what is hash of user data X to be sent?
Is hash of data X on data node N and user data X same?

is data X being transferred currently from data node N?
is data X being transferred currently to data node N?
is data X done transferring to data node N?
is data X across all data nodes consistent? (same hash)?

how much space does data node N have?
how much space does user data to send need?

send data node N location to user?
where is the location of data node N?

DATA NODES
holds data:
Metadata
Data
Directory of Metadata
Storage Space

holds function:
has storage space X?
how much storage space?
is data X across all data nodes consistent? (same hash)?
how much space does user data need?
able to receive data X?
able to send data X?
what is hash of data X?
what is hash of user data X to be sent?
Is hash of data X and user data X same?

\section{Node Internal Interface}
(check appendix for detailed pseudocode)
Frontend-Backend Interface
Via Data APIs
GET, POST, PUT, DELETE

Via Data Sync APIs
DATA SAME?

Via Data Availability APIs
DATA AVAILABLE?
DATA NODE ABLE TO RECEIVE?
DATA NODE ABLE TO SEND?

\section{Node Internal Structure}
(check appendix for detailed pseudocode)

parang this section abstracts how nodes function inside

Frontend - debugging mostly, users dont see this frontend???? or isang frontend lang ni master nakikita
Backend - storage before it goes to database? for functions? for APIs??

Inside Backend: Idea pala to categorize functions into these APIs idk if tama paggamit ko ng APIs
Network APIs - abstracted part to connect to the network
Database Sync APIs - abstracted part to keep database consistent
Database Availability APIs - abstracted part to keep database available

Database - stores shit

\subsection{Community Aspect}
- good for community since the system is expandable or customizable??
- community can see the whole framework and structure
- communities can set up their own master and data nodes
- individuals in communities can host their own data nodes (ideally master node is the institution with the data)
- ideally having multiple data nodes makes it download faster somehow
- communities can only store the data they need
- communities basically can self-expand storage, self-organize somehow the storage, and self-increase their bandwidth

>>>>

An important aspect of the proposed system is the transfer of files to other computers. To achieve that, there are network technologies and systems that need to be understood. Each layer of the network has certain features, securities, and abstraction which contributes to the overall idea of sharing files across networks. Networks Layers are the abstraction of how computers pass data to each other. Understanding this is needed to maximize the speed in which data is transferred between computers. As well as to realize where certain problems or bottlenecks later on. A network, specifically the Internet, is comprised of the following levels of abstraction. \cite{kurose}
\begin{enumerate}
    \item Level 1: Medium used to send signals (physical, electrical signals of 0
and 1), through wire or by air
    \item Level 2: Introduction of packets: Wifi, Ethernet, connecting together
different interfaces. Goal of sending a group of signals.
    \item Level 3: Introduction of networks: IP Address to uniquely identify
entities.
    \item Level 4: Management of error free data transmission: Sending a group
of messages via TCP, UDP, FTP
    \item Level 5: Abstraction of Level 4: Function calls programmers will use
to do level 4 processes.
\end{enumerate}

@@

The database is a distributed database, which will aim to utilize the best features from peer-to-peer and client-server architectures. This will also aim to store sequences. Thus the "Distributed Database for Sequences" portion of the title.

\subsubsection{Community Aspect} \label{community}
The sytem was also described as community assisted. The definition of \textbf{community} to be used here is a \textit{set of people who generally collaborate together to do research}. And the focus is the genome research community. Reemphasizing certain features from the database, that any users can upload data. This means all users in the community can contribute to the knowledge base, and contribute data to be used by the community. Another important community aspect is that institutions can increase the number of data nodes. Meaning there will be an increase in the overall storage of the database, and at the same time theoretically increase data speeds (which will be discussed more later). Frequently used local data as well will be more easily accessible (since it's on local data nodes, and should have faster access speeds). The concept of closer networks having faster speeds (discussed in the network section) is at play here. Another community aspect will be this paper, publicly describing many aspects of the structure and code. So that this concept may be further developed and even implemented by genome research communities.

@@

For the final comparisons of the base method the proposed method, the current base method (NCBI in Section \ref{NCBI}) is the go-to website for biological data and genomic data. It is currently used and is one website and one server. This points to a single point of failure\cite{seqtorr}. The section \ref{theoreticalspeed} on theoretical analysis of speed described the problem of having a bottleneck when the number of users are too many for the data bandwidth of the server.

@@
